Tables & figures for paper reporting increase of home deaths 2020

### 2021-05-04 paper_reporting_death_at_home_increase.Rmd
modified blog & paper scripts to load the workspace with visualsiations included
added figure 2 and added TIFF files

## figure for a bit less than half A4 page is approx 14*11cm
save_output_file(filename = paste0(dir_paper,"/figure1"), extensions = c(".pdf",".svg",".png"), plot = figure1, width = 28, height = 11, units = "cm", dpi = 300)
```

@@

save_output_file(filename = paste0(dir_paper,"/figure2ab_bw"), extensions = c(".pdf",".wmf",".png"), plot = figure2ab_bw, width = 20, height = 12, dpi = 300, units = "cm")
save_output_file(filename = paste0(dir_paper,"/figure2cd_bw"), extensions = c(".pdf",".wmf",".png"), plot = figure2cd_bw, width = 20, height = 12, dpi = 300, units = "cm")
```

>>>>

## figure for a bit less than half A4 page is approx 14*11cm
save_output_file(filename = paste0(dir_paper,"/figure1"), extensions = c(".pdf",".svg",".png",".tiff"), plot = figure1, width = 28, height = 11, units = "cm", dpi = 300)

save_output_file(filename = paste0(dir_paper,"/figure1_hires"), extensions = c(".png"), plot = figure1, width = 28, height = 11, dpi = 1200, units = "cm")
```

@@

save_output_file(filename = paste0(dir_paper,"/figure2ab_bw"), extensions = c(".pdf",".wmf",".png"), plot = figure2ab_bw, width = 20, height = 12, dpi = 300, units = "cm")
save_output_file(filename = paste0(dir_paper,"/figure2cd_bw"), extensions = c(".pdf",".wmf",".png"), plot = figure2cd_bw, width = 20, height = 12, dpi = 300, units = "cm")

figure2 <-
  wrap_plots(
    list(
      figure2c_bw,
      figure2d_bw
      ), 
    nrow = 1)

save_output_file(filename = paste0(dir_paper,"/figure2"), extensions = c(".pdf",".wmf",".png",".tiff"), plot = figure2, width = 20, height = 12, dpi = 300, units = "cm")

save_output_file(filename = paste0(dir_paper,"/figure2_hires"), extensions = c(".png"), plot = figure2, width = 20, height = 12, dpi = 1200, units = "cm")
```
